\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex
words and labels

In this work, we show how we can harness photometric data collected by the \TESS mission
to construct a map of Sol d, a rocky planet ‎with a radius of $6.4\times 10^6$ m
orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
star. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
the habitable zone for follow-up with other missions, it came as a great surprise
to us that data from the spacecraft could be used not only to detect Sol d but to
characterize it in detail. This is due primarily to the strong nature of the reflected
light signal originating from the planet, which 
because of complex internal optics illuminates the entirety of the \TESS detector 
during most of Sector 1 and part of Sector 2.

@@

\todo{A bit more here.}

>>>>

In this work, we show how we can harness photometric data collected by the \TESS mission
to construct a map of Sol d, a rocky planet ‎with a radius of $6.4\times 10^6$ m
orbiting near the inner edge of the habitable zone of its star, a nearby G2 main sequence
star. Although the \TESS mission promised to deliver a handful of terrestrial planets in 
the habitable zone for follow-up with other missions, it came as a great surprise
to many that data from the spacecraft could be used not only to detect Sol d but to
characterize it in detail. This is due primarily to the strong nature of the reflected
light signal originating from the planet, which 
because of complex internal optics illuminates the entirety of the \TESS detector 
during most of Sector 1 and part of Sector 2.

@@

We fit Sol d with both static and time-variable albedo maps. 
\todo{We find...} 
Future observations with \TESS will yield further information on 
the time variability of surface features on Sol d.

\todo{(habitability of Sol d, speculation on landing sites)}

The work presented here also serves as a relevant case study for future 
efforts to characterize terrestrial exoplanets. \todo{(more)}
